---
title: "`r params$title`"
author: "Jack Murzynowski"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
params:
  title: "HTML Report for Simulated GWAS Data"
  modulate: NULL
  parameter_used: NULL
  causal_snps: NULL
  manhattan_png: NULL
  bonferroni: NULL
  fdr: NULL
  qq_png: NULL
  inflation: NULL
  roc_png: NULL
  auc: NULL
  general_stats: NULL
  max_F: NULL
  power_thresh: NULL
---

```{r setup, include=FALSE}
better_DT <- function(data_use,
                      target = "column",
                      multi_target = FALSE,
                      rownames = FALSE,
                      class = "display",
                      pageLength = 10,
                      lengthMenu = list(c(10, 25, 50, 100, -1), c(10, 25, 50, 100, "All")),
                      info = TRUE,
                      search_box = TRUE,
                      download_button = TRUE,
                      col_vis_button = TRUE, 
                      hidden_cols = NULL, 
                      rowReorder = FALSE,
                      row_group_col = NULL,
                      row_group_mean_cols = c(NULL),
                      collapse_group_default = TRUE,
                      fix_left_column = NULL,
                      fix_right_column = NULL,
                      fix_header = FALSE,
                      col_head_colour = list(NULL),
                      col_head_font_size = 1,
                      col_head_font_rotate = 0,
                      escape = TRUE,
                      state = NULL){
  
  
  # Determine target to select
  if(multi_target){
    selection_mode <- "multiple"
  } else {
    selection_mode <- "single"
  }
  # Determine fixed columns
  if(!is.null(fix_left_column) | !is.null(fix_right_column)){
    fixedCols <- list(leftColumns = fix_left_column, rightColumns = fix_right_column)
  } else {
    fixedCols <- FALSE
  }
  
  # Check column visibility options
  if(!is.null(hidden_cols)){
    col_vis_button <- TRUE
    columnDefs <- list(list(targets = c(hidden_cols), visible = FALSE))
  } else {
    columnDefs <- list(list(targets = "_all", className = "dt-center"))
  }
  
  # Set buttons to add
  buttons <- list()
  if(col_vis_button){
    datausecolnum <- ncol(data_use) - 1
    mxdatausecolnum <- as.numeric(c(0:datausecolnum))
    buttons <- list.append(buttons,list(extend = 'colvis', columns = mxdatausecolnum))
    buttons <- list.append(buttons,list(extend = "colvisGroup",text="Show All",show=":hidden"))
  }
  if(download_button){
    buttons <- list.append(buttons,list(extend = 'collection',buttons = c('csv', 'excel', 'pdf','print'), text = 'Download'))
  }
  
  # Sort out dom
  dom <- "r<\"datatables-scroll\"t>pli"
  if(search_box){
    dom <- paste0("f",dom)
  }
  if(download_button | col_vis_button){
    dom <- paste0("B",dom)
  }
  
  # Format the JS headercallback (include initial CSS to format columns and search boxes)
  headerCallback <- c("function(thead, data, start, end, display){",
                      "  var DTscroll = $('.datatables-scroll');",
                      "  DTscroll.css({'overflow-x': 'auto', 'width': '100%'});",
                      "  var td = $('.datatables-scroll thead tr td');",
                      "  td.css({'position': 'sticky', 'background-color': '#FFFFFF'});",
                      "  var factor_td = td.filter(function (d) {
                          return($(this)[0].attributes[0].value == 'factor');
                         })",
                      "  factor_td.each(function(d){
                          var factor_dropdown = factor_td[d].childNodes[3].childNodes[2].childNodes[1];
                          var new_dropdown = factor_dropdown.childNodes[0];
                          factor_dropdown.setAttribute('style','background-color:transparent; border:transparent; box-shadow:none')
                          new_dropdown.setAttribute('style','width:fit-content; background-color:white; border:1px solid rgba(0, 0, 0, 0.15); border-radius:4px; box-shadow:0 6px 12px rgba(0, 0, 0, 0.175); max-height:100px');
                         });")
  
  if(!is.null(col_head_colour[[1]])){
    init_code_for_colour <- paste0("var th = $('.datatables-scroll thead tr th');")
    if(data.class(col_head_colour[[1]])=="character"){
      col_head_colour[[1]] <- which(colnames(data_use) %in% col_head_colour[[1]])-1
    }
    for(i in 1:length(col_head_colour[[1]])){
      init_code_for_colour <- rbind(init_code_for_colour,paste0("  th[",col_head_colour[[1]][i],"].setAttribute('style','color: ",col_head_colour[[2]][i],"');"))
    }
    code_for_col_colour <- paste(init_code_for_colour, collapse = " ")
    headerCallback <- c(headerCallback,
                        code_for_col_colour)
  }
  
  if(col_head_font_size != 1){
    code_for_col_size <- paste0("  $(thead).css('font-size', '",col_head_font_size,"em');")
    headerCallback <- c(headerCallback,
                        code_for_col_size)
  }
  if(col_head_font_rotate != 0){
    col_head_font_rotate <- abs(90-col_head_font_rotate)
    code_for_col_rotate <- paste0("      'transform': 'rotate(",col_head_font_rotate,"deg)',")
    headerCallback <- c(headerCallback,
                        "  var $ths = $(thead).find('th');",
                        "  $ths.css({'vertical-align': 'top', 'padding': '4px 0px',",
                        "          'transform': 'rotate(180deg)', 'border': 'none'});",
                        "  var betterCells = [];",
                        "  $ths.each(function(){",
                        "    var cell = $(this);",
                        "    var newDiv = $('<div>', {width: '5px', float: 'left'});",
                        "    var newInnerDiv = $('<div>', {text: cell.text()});",
                        "    newDiv.css({margin: 'auto'});",
                        "    newInnerDiv.css({",
                        "      'writing-mode': 'vertical-rl',",
                        "      'white-space': 'nowrap',",
                        "      'text-align': 'left',",
                        "      'transform-origin': 'top left',",
                        code_for_col_rotate,
                        "      'overflow': 'visible'",
                        "    });",
                        "    newDiv.append(newInnerDiv);",
                        "    betterCells.push(newDiv);",
                        "  });",
                        "  $ths.each(function(i){",
                        "    $(this).html(betterCells[i]);",
                        "  });"
    )
  }
  headerCallback <- c(headerCallback,"}")
  
  # Sort out row grouping
  
  
  if(!is.null(row_group_col)){
    # Get the group index and name
    if(data.class(row_group_col)=="character"){
      row_group_name <- row_group_col
      row_group <- which(colnames(data_use)==row_group_col)
    } else {
      row_group <- row_group_col
      row_group_name <- colnames(data_use)[row_group]
    }
    # Reorder the data to ensure correct grouping
    data_use <- data_use[order(data_use[,row_group]),]
    
    # Set means if required
    # Create grouping code
    avg_code <- NULL
    cell_pos <- NULL
    if(!is.null(row_group_mean_cols)){
      if(data.class(row_group_mean_cols)=="character"){
        mean_cols <- which(colnames(data_use) %in% row_group_mean_cols)
      } else {
        mean_cols <- row_group_mean_cols
      }
      # Calculate means
      for(i in 1:ncol(data_use)){
        if(i %in% mean_cols){
          col_average <- mean_cols[which(mean_cols == i)]
          avg_code <- c(avg_code,
                        paste0("let col_",col_average,"_avg = rows.data().pluck(",col_average,").filter(Number).reduce((a, b) => a + b * 1, 0) / rows.data().pluck(",col_average,").filter(Number).length;"))
          cell_pos <- c(cell_pos,
                        paste0("addCell(tr, col_",col_average,"_avg.toFixed(4),align = 'right');"))
        } else {
          avg_code <- c(avg_code,
                        paste0("let col_",i,"_avg = '';"))
          cell_pos <- c(cell_pos,
                        paste0("addCell(tr, col_",i,"_avg);"))
        }
      }
    }
    
    # Create the callback
    groupCallback <- paste0("{endRender: null,
                         startRender: function (rows, group) {
                          function addCell(tr, content, colSpan = 1,align = 'left') {
                            let td = document.createElement('th');
                            td.colSpan = colSpan;
                            td.setAttribute('style','text-align:' + align);
                            td.textContent = content;
                            tr.appendChild(td);
                          }
                          let tr = document.createElement('tr');
                          ",paste(avg_code,collapse = " 
                          "),"
                          addCell(tr, '",row_group_name," group: ' + group, ",1,");
                          ",paste(cell_pos,collapse = " 
                          "),"
                          return tr;
                        },
                        dataSrc: ",row_group,"
                      }")
    callback <- c("table.on('click', 'tr.dtrg-group', function () {",
                  "  var rowsCollapse = $(this).nextUntil('.dtrg-group');",
                  "  $(rowsCollapse).toggleClass('hidden');",
                  "});")
    if(collapse_group_default){
      callback <- c(callback,"table.on('init', () => $('.dtrg-group').trigger('click'));")
    }
    js_callback <- JS(callback)
    rownames <- TRUE
  } else {
    groupCallback <- NULL
    js_callback <- JS("")
  }
  
  # Sort out the state
  if(!is.null(state)){
    # Reorder columns
    if(isTruthy(state$col_order)){
      data_use <- data_use[,state$col_order+1]
    }
    # Hide columns
    if(any(!is.null(state$col_vis))){
      if(any(!state$col_vis)){
        hidden_columns <- (which(!state$col_vis)-1)
        columnDefs <- list(list(targets = c(hidden_columns), visible = FALSE))
      }
    }
    # Set page length
    if(!is.null(state$table_length)){
      pageLength <- state$table_length
    }
    # Set order
    stateCallback <- state$filter_order
  } else {
    stateCallback <- NULL
  }
  
  # Create the datatable
  datatable(data = data_use,
            rownames = rownames,
            class = class,
            filter = "top",
            selection = list(mode = selection_mode, target = target),
            extensions = c('Buttons','ColReorder', 'RowReorder','RowGroup','FixedColumns','FixedHeader'),
            escape = escape,
            options = list(
              headerCallback = JS(headerCallback),
              columnDefs = columnDefs,
              fixedColumns = fixedCols,
              fixedHeader = fix_header,
              rowGroup = JS(groupCallback),
              dom = dom,
              pageLength = pageLength,
              lengthMenu = lengthMenu,
              info = info,
              colReorder = TRUE,
              rowReorder = rowReorder,
              buttons = buttons,
              stateSave = TRUE,
              order = JS(stateCallback),
              stateDuration = -1
            ),
            callback = js_callback
  )
}
```

# Simulation parameters

This data stems from runs modulating **`r params$modulate`**. Below is the table of the parameters used in this run:
```{r echo=FALSE, results='asis'}
if (!is.null(params$parameter_used)) {
  knitr::kable(params$parameter_used)
}
```


# Results

## Causal SNP Associations

Below is a table of all the causal SNPs and their respective association values:
```{r echo=FALSE, results='asis'}
if (!is.null(params$causal_snps)) {
  better_DT(data = params$causal_snps,search_box = F,col_vis_button = T,pageLength = nrow(params$causal_snps),
            hidden_cols = c(4:8,10:13,18:19))
}
```

## Manhattan Plot
```{r echo=FALSE, results='asis'}
if (!is.null(params$manhattan_png)) {
  knitr::include_graphics(params$manhattan_png)
}
```
The blue line is the Bonferroni corrected pval (`r sprintf("%.3f", params$bonferroni)`), the red line is the FDR pval (`r sprintf("%.3f", params$fdr)`).
Causal SNPs are highlighted based off their relation to the pvalues. 

- Red = SNPs below the FDR
- Orange = SNPs above FDR but below Bonferroni
- Blue = SNPs above Bonferroni

## QQ Plot
```{r echo=FALSE, results='asis'}
if (!is.null(params$qq_png)) {
  knitr::include_graphics(params$qq_png)
}
```
The same colour coding as before, the inflation factor = **`r params$inflation`**

## ROC Curve
```{r echo=FALSE, results='asis'}
if (!is.null(params$roc_png)) {
  knitr::include_graphics(params$roc_png)
}
```
The AUC = **`r params$auc`**

# Statistics

Some general stats around the simulation are below:

## General Stats
```{r echo=FALSE, results='asis'}
if (!is.null(params$general_stats)) {
  knitr::kable(params$general_stats)
}
```

## Max F-Score
```{r echo=FALSE, results='asis'}
if (!is.null(params$max_F)) {
  knitr::kable(params$max_F)
}
```

## Power Thresholds
```{r echo=FALSE, results='asis'}
if (!is.null(params$power_thresh)) {
  knitr::kable(params$power_thresh)
}
```
